---
title: "Confusion Matrix "
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(shinyMatrix)
library(Matrix)
library(epitools)
library(caret)
library(e1071)

```

```{r, echo=FALSE}
sidebarPanel(h6("Edit the Predictive Classes (in Rows) and Actual Classes(in Columns)"),
  uiOutput("mat"),
  uiOutput("pos"),
  plotOutput("CMVis"),
  downloadButton("downloadPlot", "Download Confusion Matrix Plot"),
  downloadButton("downloaddata", "Download dataset"))
mainPanel(
  #h6("Edit the Predictive Classes (in Rows) and Actual Classes(in Columns)"),
 # uiOutput("mat"),
 # uiOutput("pos"),
#plotOutput("CMVis"),
  verbatimTextOutput("results"),
  
  h6("", tags$img(src ="K.JPG", height= 400, width=400))

  
)

output$mat <- renderUI({
     matrixInput(
       "myMatrix",
       value = matrix(c(5,1,1,3),2,2,dimnames = list(c("Class1","Class2"),c("Class1","Class2"))),
       
       rows = list(names= TRUE,editableNames = TRUE),
       cols = list( names = TRUE,editableNames = TRUE),
       copy = TRUE,
       paste = TRUE,
       class = 'numeric'
     )
   })


output$pos <- renderUI({
     CT =  matrix(input$myMatrix,nrow = 2, ncol = 2)
     row.names(CT) = row.names(input$myMatrix)
     colnames(CT) = colnames(input$myMatrix)
     dataset = expand.table(CT)
     colnames(dataset)= c("Predicted","Actual")
     selectInput("positive",label = "Select the Positive Class",choices = c(levels(dataset$Predicted)))
})
output$results <- renderPrint({
     CT =  matrix(input$myMatrix,nrow = 2, ncol = 2)
     
     row.names(CT) = row.names(input$myMatrix)
     colnames(CT) = colnames(input$myMatrix)
     dataset = expand.table(CT)
     colnames(dataset)= c("Predicted","Actual")
    
     print(confusionMatrix(dataset$Predicted,dataset$Actual,positive = input$positive ))
     
})
output$CMVis <- renderPlot({
     CT =  matrix(input$myMatrix,nrow = 2, ncol = 2)
     row.names(CT) = row.names(input$myMatrix)
     colnames(CT) = colnames(input$myMatrix)
     dataset = expand.table(CT)
     colnames(dataset)= c("Predicted","Actual")
     
ctable <- as.table(matrix(CT, nrow = 2, byrow = FALSE))
fourfoldplot(ctable, color = c("#CC6666", "#99CC99"),
             conf.level = 0, margin = 1, main = "Confusion Matrix")

  # trellis.par.set(caretTheme())
  # liftobj = lift(Actual~Predicted,data =  dataset)
 #  plot(liftobj)
 #  plot(liftobj,auto.key = list(columns =1,lines = TRUE,points = FALSE))
})


datasetInput1 <- reactive({
      CT =  matrix(input$myMatrix,nrow = 2, ncol = 2)
     row.names(CT) = row.names(input$myMatrix)
     colnames(CT) = colnames(input$myMatrix)
     dataset = expand.table(CT)
     colnames(dataset)= c("Predicted","Actual")
     dataset =  dataset


   })
   output$downloaddata <- downloadHandler(
     filename = function() {
       filetitle = paste("dataset")
       paste(filetitle, ".csv", sep = "")
     },
     content = function(file) {

       write.csv(datasetInput1(), file, row.names = FALSE)
     }
   )
   
  output$downloadPlot<- downloadHandler(
     filename = function() {
       paste("ConfusionMatPlot", ".png", sep = "")
     },
     content = function(file) {
       png(file)
        CT =  matrix(input$myMatrix,nrow = 2, ncol = 2)
     row.names(CT) = row.names(input$myMatrix)
     colnames(CT) = colnames(input$myMatrix)
     dataset = expand.table(CT)
     colnames(dataset)= c("Predicted","Actual")
     
ctable <- as.table(matrix(CT, nrow = 2, byrow = FALSE))
fourfoldplot(ctable, color = c("#CC6666", "#99CC99"),
             conf.level = 0, margin = 1, main = "Confusion Matrix")
       dev.off()
     }) 